Abstract Data Type Inference

### 2015-03-10 inference.tex
Added notion of “weight”.

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of $h$ is the maximal size of a
subset of $O$ for which each pair of operations is unordered. The \emph{width}
of a history set is the maximal width of its elements. Width-$1$ histories are
\emph{sequential}. An operation $o \in \rng(m)$ is a \emph{match target}, and
the set $\set{ o' \in O : m(o') = o}$ of operations targeting $o$ is a
\emph{match}. We assume targets target themselves: $o \in \set{ o' \in O :
m(o') = o}$.

>>>>

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum size of an
unordered subset of its operations. The \emph{width} of a history set is the
maximal width of its elements. Width-$1$ histories are \emph{sequential}. An
operation $o \in \rng(m)$ is a \emph{match target}, and the set $\set{ o' \in O
: m(o') = o}$ of operations targeting $o$ is a \emph{match}. We assume targets
target themselves: $m(o) = o$ for $o \in \rng(m)$. The \emph{weight} of $h$ is
the amount $|\rng(m)|$ of matches.
